Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-04-20 paper/gen-graph-unconnected-heatmap.tex
More gratuitous mucking around with the figures
Handle headers on first line
Green / blue instead of blood splatters

%% Tue 12 Apr 2016 14:19:16 AEST

@@

  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffffff9f7dff9f7dff9f7dffac88ff9f7d%
  ff9f7dffac88ff9576ff95768b0000ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffcf1d45ffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffac88ffffffca1941ffffff%
  ffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffac88ffffffc7173effffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ffffffffffffffffffffac88c7173effffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffac88ffffffc6163dffffffffffff%
  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffac88ffffffffffffffffffffac88ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffc6163effffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ff9576ffffffffac88c7173fffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffffffff9f7dffac88ffffffffffffc1133affffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffff%
  ffffffc8183fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ffac88ffffffffac88ffac88%
  ffffffffffffffffffffffffffffffffffffc8183fffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffff%
  ffffffffac88ffac88ffffffffffffffffffffffffffac88ffffffffac88ff9f7dc6163effffffffffffffffffffffff%
  ffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  c8183fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffac88%
  ffffffffffffffac88ffffffffac88c4153cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffffffc4143cffffffffffffffffffffffffffffff%
  ffffffffac88ffffffffffffffac88ffffffffac88ffac88ffffffffac88ffac88ff9f7dffac88ff9f7dffffffc3143b%
  ffffffffac88ffffffffac88ffffffffffffffffffffac88ffac88ffffffffac88ffffffffac88ffffffffffffff9f7d%
  ffac88ffffffffffffff9f7dc1133affffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ffffffffffffffffffffac88ffffffffffffffac88ffffffffffffffffffffac88ffffff%
  ffffffffac88ffac88ffffffffac88ffffffffffffffac88ffac88c4153cffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffff9576ffffffffffffffffffffffffffffffffffffffffffffac88ff9f7dffac88c2133affffff%
  ffac88ffffffffffffffffffffffffffffffffac88ffac88ffac88ffffffffac88ffffffffac88ffffffff9576ffac88%
  ff9576ffffffff9f7dc6163dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffffff%
  ffac88ffffffffac88ffac88ffffffffac88ffac88ff846ec01239ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffff9f7d%
  ffffffffffffffffffffac88ffac88ffffffffac88ffffffff9576ffffffffac88ffac88ffffffc4153cffffffffffff%
  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
  ffffffff9f7dffffffffffffffffffffac88ffffffffffffffffffffac88ff9f7dff9f7dffffffffffffffac88ff9f7d%
  ff9f7dffffffbd0f36ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffac88ffffffff9576ffffffffac88%
  ff9f7dffac88ff9576ff9f7dff9576ffffffffac88c2133affffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffff9f7dffffffffffffffac88ffffffffffffffffffffac88%
  ffac88ffffffff9f7dffffffffac88ffac88ff9576ffffffffac88ff9f7dff9576ffffffc1133affffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffffff%
  ff9f7dffffffffffffffffffffac88ffffffffffffffac88ff9f7dff9576ffffffffac88ffffffff9f7dff9f7dff8c72%
  ff9f7dc01238ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffff%
  ffffffffffffffffffffffffffffffffffffff9f7dffac88ffac88ffffffffffffff9f7dffffffff9576ffac88ffac88%
  ffac88ff9f7dff9576ff846effac88ffac88c1133affffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffac88ffffffffffffffffffffffffffac88ffffffffffffffffffffac88ff9f7dffffffffffffffac88ff9f7d%
  ffffffff9f7dff9576ff9f7dffac88ff9576ffac88ff9f7dff846eff8c72ff8c72c3143bffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffac88ff9f7dffffffffac88ffac88ffac88%
  ffffffff9f7dff9f7dff9f7dff9f7dffac88ff9f7dffac88ffac88ffac88ff846eff9576ff9f7dff9f7dff9f7dff9576%
  c11239ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffff%
  ffffffffac88ffac88ffffffffffffff9f7dffac88ffffffffffffffac88ffac88ffac88ff9576ffac88ffffffffac88%
  ff9576ff9576ff846eff846effffffbd1036ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffffffffac88ffac88ffac88ffac88ffac88ff9576ff846eff9f7dffffffff9f7d%
  ffffffffffffff9f7dffffffff9f7dffffffff9576ff9576ffac88ffac88c01239ffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffff9576%
  ffac88ffac88ff9f7dff846effffffffac88ff846eff9576ff9576ffac88ff8c72ff9f7dff8c72ffffffff9f7dbf1138%
  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffff9576ffffffffac88ffffff%
  ffffffffac88ffffffffac88ffffffff9576ff9f7dffac88ff8c72ff9576ff8c72ffac88ffac88ff9f7dff9f7dffac88%
  ffffffff8c72ff846effac88c11239ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ffffffff9f7dff9f7dffac88ffffffff9f7dff9f7dffac88ffac88ff8c72ff9f7dff9f7d%
  ff8c72ff9576ff8c72ff9f7dff8c72ff9f7dff846eff8c72ff7e6cc11239ffffffffffffffffffffffffffffffffffff%
  ffffffffffffffac88ffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffac88ffac88ff9f7dffac88%
  ffac88ffac88ff9f7dff7e6cffac88ff9f7dffffffff9576ff9f7dff9576ff9f7dff9576ffac88fb605fc2133bffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffff%
  ffffffffffffffffffffac88ffac88ffffffffffffffffffffffffffffffffac88ffffffffffffff9f7dffac88ffac88%
  ffffffffac88ffffffff846eff846eff9576ffac88ff846effffffff8c72ff9576ff9f7dff9576ff846effac88ff7869%
  ff7e6cff9576ff8c72c4153cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffac88%
  ffffffffffffffffffffffffff9f7dff9f7dffac88ffffffffac88ff846eff846eff9576ff7869ffffffff8c72ffffff%
  ff8c72ffac88ff8c72ff7e6cff9576ff8c72ff846eff9576c01239ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffff9f7dffffffffffff%
  ffffffffffffffffffffffffffac88ffffffffac88ffffffffffffff9f7dffffffffac88ffac88ff9f7dffac88ff9576%
  ffac88ffffffff846eff9f7dff8c72ff846eff7e6cff9f7dff7869ff9576ff7e6cff8c72ff7e6cc1133affffffffffff%
  ffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffac88ffffffff9f7dffffffffac88ff9f7dff9576%
  ff8c72ff9576ffac88ff7e6cffac88ff9f7dffac88ff846eff8c72ff9f7dff9576ff9576ff7367ff6f65ff846eff8c72%
  ff7e6cff7e6cc3143bffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffffffffac88%
  ffffffffac88ffac88ff9576ffac88ffffffffac88ffac88ff9576ff9f7dffac88ff7869ffac88ff9f7dff8c72ff7869%
  ff8c72ff9f7dff7367ff7e6cff9576ff6f65ff7e6cc6163dffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffffffffac88ffffffffffffffac88ffffff%
  ffffffffffffffffffffffffff9576ffffffffffffff9f7dffac88ff9f7dffac88ff9576ff9f7dffac88ff846eff7e6c%
  ff7869ff846effac88ffac88ffac88ff9f7dff7e6cffac88ff846eff7869ff8c72ff8c72c4153cffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffac88ffffffffac88ffac88ffac88ffffffffac88ffffffffac88ffac88ffffffffac88ff8c72ffffffffffff%
  ff8c72ff9f7dff9f7dff9576ff7869ff9f7dff7e6cff7869ff8c72ffac88ff7869ffac88ff8c72ff8c72ff7869ff7e6c%
  ff9576c4153cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffac88ff9f7dff9f7dffffffffac88ffffff%
  ff9f7dffac88ff8c72ff8c72ff9576ffffffff9f7dffac88ff846eff7869ff9576ffffffff846eff9576ff8c72ff7869%
  ff846eff9576ff7e6cff6b63ff7e6cff8c72cb1a41ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffac88ffac88ffffffffffffffffffffac88ffffffffac88ffffffffffffffffffffac88ffffffffffffffffffffac88%
  ff9f7dff9f7dff9f7dff9576ffac88ffffffff8c72ff9f7dffac88ff8c72ff9f7dff8c72ff9576ff7e6cff7869ffac88%
  ff8c72ff9576ff7869ff846eff7e6cff6b63ffac88ff9576ff846eff9576ff8c72c8183fffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffff%
  ffffffffffffffac88ffffffffac88ffffffffffffffffffffffffffac88ffac88ffac88ffffffffac88ff9f7dffac88%
  ffffffffffffffffffffffffffffffffac88ffac88ffffffff846effffffffffffffac88ff9f7dff7869ff8c72ff8c72%
  ff9576ff8c72ff846eff9576ff7e6cff846eff846eff7e6cff7367ff7e6cff9576ff7e6cff8c72ff9f7dff9f7dff7e6c%
  c8183fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffac88ffffffffac88ffffffffffffffffffffac88ffffffffffffff9f7dffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffac88ffffffffffffffffffffffffff9f7dff9f7dffffffffac88ff9576ffac88ffac88%
  ff9f7dffffffffac88ff846effffffffac88ff9f7dff846eff6f65ff7367ff846eff9576ff8c72ff846eff846eff7e6c%
  ff9576ff846eff8c72ff8c72ff6b63c8183fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ffffffffffffffac88ffffffffac88ffffffffac88ffffffffffffffffffffac88ffffff%
  ffffffffffffffac88ff7e6cff846eff9576ff846eff9f7dff846eff7e6cff9f7dff7e6cff7869ff8c72ff7e6cff9f7d%
  ff846eff8c72ff9f7dffac88ff9576ff846eff8c72ff7367ff846effac88c7173effffffffffffffffffffffffffffff%
  ffffffffffffffffffffac88ffffffffffffffffffffffffffffffffffffffffffffac88ffac88ffffffffac88ffac88%
  ffac88ffffffffffffffffffffac88ffac88ff9576ff9576ffac88ffac88ff9576ff9576ffac88ff9f7dff9576ff9576%
  ff9576ff7e6cff9576ff7e6cff7e6cff846eff8c72ff9576ff7869ff8c72ff7869ff7e6cfd6561fe6862ff7e6cc6163e%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffffffffffffffffffffffff%
  ff9f7dffffffffffffffac88ffffffffac88ff9f7dffac88ffffffffffffffac88ffac88ff8c72ffac88ff846effac88%
  ff846eff7e6cff8c72ff7e6cff7e6cff846eff8c72fd6561ff7869ff7869ff9576ff7e6cff9576ff8c72ff7e6cffffff%
  ff9576ff7869ff8c72ff7367c8183fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffac88ffffffffac88ffffffffffffffffff%
  ffffffffffffff9f7dffac88ffffffffffffffffffffffffffac88ffffffffffffffac88ffac88ff9f7dff8c72ffac88%
  ffac88ff9f7dffffffff7e6cff9f7dffac88ff9576ff846eff7e6cfe6862ff846eff7869ff8c72ff6f65ff7367ff9576%

>>>>

%% Wed 20 Apr 2016 12:04:42 AEST

@@

  ffffffffffffffffffffffffffffffffffffffffff9cea9cffffff9cea9cffffff85de9185de9185de919cea9c85de91%
  85de919cea9c79d48d79d48d000080ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffff235f81ffffffffffffffffffffffffffffffffffff%
  ffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffff85de919cea9cffffff255881ffffff%
  ffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffff9cea9cffffff265481ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffff9cea9cffffffffffffffffff9cea9c265481ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffff9cea9cffffff265381ffffffffffff%
  ffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffff9cea9cffffffffffffffffff9cea9cffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffff265381ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffff9cea9c79d48dffffff9cea9c255581ffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffff%
  ffffffffffffffffffffffffffffffffffff9cea9cffffff85de919cea9cffffffffffff274d81ffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffff%
  ffffff255681ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffff9cea9c9cea9cffffff9cea9c9cea9c%
  ffffffffffffffffffffffffffffffffffff255581ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffff%
  ffffff9cea9c9cea9cffffffffffffffffffffffff9cea9cffffff9cea9c85de91265381ffffffffffffffffffffffff%
  ffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  255681ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c9cea9c9cea9c%
  ffffffffffff9cea9cffffff9cea9c265181ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffff%
  ffffffffffff9cea9cffffffffffffffffff9cea9cffffffffffffffffff275081ffffffffffffffffffffffffffffff%
  ffffff9cea9cffffffffffff9cea9cffffff9cea9c9cea9cffffff9cea9c9cea9c85de919cea9c85de91ffffff274f81%
  ffffff9cea9cffffff9cea9cffffffffffffffffff9cea9c9cea9cffffff9cea9cffffff9cea9cffffffffffff85de91%
  9cea9cffffffffffff85de91274d81ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffff9cea9cffffffffffffffffff9cea9cffffffffffff9cea9cffffffffffffffffff9cea9cffffff%
  ffffff9cea9c9cea9cffffff9cea9cffffffffffff9cea9c9cea9c265181ffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffff79d48dffffffffffffffffffffffffffffffffffffffffff9cea9c85de919cea9c274e81ffffff%
  9cea9cffffffffffffffffffffffffffffff9cea9c9cea9c9cea9cffffff9cea9cffffff9cea9cffffff79d48d9cea9c%
  79d48dffffff85de91265381ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff85de91ffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff85de91ffffffffffff%
  9cea9cffffff9cea9c9cea9cffffff9cea9c9cea9c6cc78c284c81ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff85de91%
  ffffffffffffffffff9cea9c9cea9cffffff9cea9cffffff79d48dffffff9cea9c9cea9cffffff265181ffffffffffff%
  ffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff%
  ffffff85de91ffffffffffffffffff9cea9cffffffffffffffffff9cea9c85de9185de91ffffffffffff9cea9c85de91%
  85de91ffffff274881ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffff9cea9cffffff79d48dffffff9cea9c%
  85de919cea9c79d48d85de9179d48dffffff9cea9c274e81ffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffff85de91ffffffffffff9cea9cffffffffffffffffff9cea9c%
  9cea9cffffff85de91ffffff9cea9c9cea9c79d48dffffff9cea9c85de9179d48dffffff274d81ffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9c9cea9cffffffffffffffffff%
  85de91ffffffffffffffffff9cea9cffffffffffff9cea9c85de9179d48dffffff9cea9cffffff85de9185de9172cd8d%
  85de91284b81ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff%
  ffffffffffffffffffffffffffffffffffff85de919cea9c9cea9cffffffffffff85de91ffffff79d48d9cea9c9cea9c%
  9cea9c85de9179d48d6cc78c9cea9c9cea9c284d81ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffff9cea9cffffffffffffffffffffffff9cea9cffffffffffffffffff9cea9c85de91ffffffffffff9cea9c85de91%
  ffffff85de9179d48d85de919cea9c79d48d9cea9c85de916cc78c72cd8d72cd8d274f81ffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffff9cea9c85de91ffffff9cea9c9cea9c9cea9c%
  ffffff85de9185de9185de9185de919cea9c85de919cea9c9cea9c9cea9c6cc78c79d48d85de9185de9185de9179d48d%
  284d81ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffff%
  ffffff9cea9c9cea9cffffffffffff85de919cea9cffffffffffff9cea9c9cea9c9cea9c79d48d9cea9cffffff9cea9c%
  79d48d79d48d6cc78c6cc78cffffff274881ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffff9cea9cffffffffffffffffff9cea9c9cea9c9cea9c9cea9c9cea9c79d48d6cc78c85de91ffffff85de91%
  ffffffffffff85de91ffffff85de91ffffff79d48d79d48d9cea9c9cea9c284b81ffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffff79d48d%
  9cea9c9cea9c85de916cc78cffffff9cea9c6cc78c79d48d79d48d9cea9c72cd8d85de9172cd8dffffff85de91284a81%
  ffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffff79d48dffffff9cea9cffffff%
  ffffff9cea9cffffff9cea9cffffff79d48d85de919cea9c72cd8d79d48d72cd8d9cea9c9cea9c85de9185de919cea9c%
  ffffff72cd8d6cc78c9cea9c284c81ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffff9cea9cffffff85de9185de919cea9cffffff85de9185de919cea9c9cea9c72cd8d85de9185de91%
  72cd8d79d48d72cd8d85de9172cd8d85de916cc78c72cd8d67c28b284c81ffffffffffffffffffffffffffffffffffff%
  ffffffffffff9cea9cffffffffffffffffffffffffffffff9cea9cffffff9cea9cffffff9cea9c9cea9c85de919cea9c%
  9cea9c9cea9c85de9167c28b9cea9c85de91ffffff79d48d85de9179d48d85de9179d48d9cea9c4aa787274e81ffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffff%
  ffffffffffffffffff9cea9c9cea9cffffffffffffffffffffffffffffff9cea9cffffffffffff85de919cea9c9cea9c%
  ffffff9cea9cffffff6cc78c6cc78c79d48d9cea9c6cc78cffffff72cd8d79d48d85de9179d48d6cc78c9cea9c62bd8b%
  67c28b79d48d72cd8d265181ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff9cea9cffffff9cea9c%
  ffffffffffffffffffffffff85de9185de919cea9cffffff9cea9c6cc78c6cc78c79d48d62bd8bffffff72cd8dffffff%
  72cd8d9cea9c72cd8d67c28b79d48d72cd8d6cc78c79d48d284b81ffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffff85de91ffffffffffff%
  ffffffffffffffffffffffff9cea9cffffff9cea9cffffffffffff85de91ffffff9cea9c9cea9c85de919cea9c79d48d%
  9cea9cffffff6cc78c85de9172cd8d6cc78c67c28b85de9162bd8b79d48d67c28b72cd8d67c28b274d81ffffffffffff%
  ffffffffffffffffffffffffffffff9cea9c9cea9cffffffffffff9cea9cffffff85de91ffffff9cea9c85de9179d48d%
  72cd8d79d48d9cea9c67c28b9cea9c85de919cea9c6cc78c72cd8d85de9179d48d79d48d5eb98a5ab5896cc78c72cd8d%
  67c28b67c28b274f81ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffffffffff9cea9c%
  ffffff9cea9c9cea9c79d48d9cea9cffffff9cea9c9cea9c79d48d85de919cea9c62bd8b9cea9c85de9172cd8d62bd8b%
  72cd8d85de915eb98a67c28b79d48d5ab58967c28b265381ffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffff9cea9c9cea9cffffffffffff9cea9cffffffffffff9cea9cffffff%
  ffffffffffffffffffffffff79d48dffffffffffff85de919cea9c85de919cea9c79d48d85de919cea9c6cc78c67c28b%
  62bd8b6cc78c9cea9c9cea9c9cea9c85de9167c28b9cea9c6cc78c62bd8b72cd8d72cd8d265181ffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffff%
  ffffff9cea9cffffff9cea9c9cea9c9cea9cffffff9cea9cffffff9cea9c9cea9cffffff9cea9c72cd8dffffffffffff%
  72cd8d85de9185de9179d48d62bd8b85de9167c28b62bd8b72cd8d9cea9c62bd8b9cea9c72cd8d72cd8d62bd8b67c28b%
  79d48d275081ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffff9cea9c85de9185de91ffffff9cea9cffffff%
  85de919cea9c72cd8d72cd8d79d48dffffff85de919cea9c6cc78c62bd8b79d48dffffff6cc78c79d48d72cd8d62bd8b%
  6cc78c79d48d67c28b56b28967c28b72cd8d245981ffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  9cea9c9cea9cffffffffffffffffff9cea9cffffff9cea9cffffffffffffffffff9cea9cffffffffffffffffff9cea9c%
  85de9185de9185de9179d48d9cea9cffffff72cd8d85de919cea9c72cd8d85de9172cd8d79d48d67c28b62bd8b9cea9c%
  72cd8d79d48d62bd8b6cc78c67c28b56b2899cea9c79d48d6cc78c79d48d72cd8d255581ffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffff%
  ffffffffffff9cea9cffffff9cea9cffffffffffffffffffffffff9cea9c9cea9c9cea9cffffff9cea9c85de919cea9c%
  ffffffffffffffffffffffffffffff9cea9c9cea9cffffff6cc78cffffffffffff9cea9c85de9162bd8b72cd8d72cd8d%
  79d48d72cd8d6cc78c79d48d67c28b6cc78c6cc78c67c28b5eb98a67c28b79d48d67c28b72cd8d85de9185de9167c28b%
  255681ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  9cea9cffffff9cea9cffffffffffffffffff9cea9cffffffffffff85de91ffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffff9cea9cffffffffffffffffffffffff85de9185de91ffffff9cea9c79d48d9cea9c9cea9c%
  85de91ffffff9cea9c6cc78cffffff9cea9c85de916cc78c5ab5895eb98a6cc78c79d48d72cd8d6cc78c6cc78c67c28b%
  79d48d6cc78c72cd8d72cd8d56b289255581ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffff9cea9cffffffffffff9cea9cffffff9cea9cffffff9cea9cffffffffffffffffff9cea9cffffff%
  ffffffffffff9cea9c67c28b6cc78c79d48d6cc78c85de916cc78c67c28b85de9167c28b62bd8b72cd8d67c28b85de91%
  6cc78c72cd8d85de919cea9c79d48d6cc78c72cd8d5eb98a6cc78c9cea9c265481ffffffffffffffffffffffffffffff%
  ffffffffffffffffff9cea9cffffffffffffffffffffffffffffffffffffffffff9cea9c9cea9cffffff9cea9c9cea9c%
  9cea9cffffffffffffffffff9cea9c9cea9c79d48d79d48d9cea9c9cea9c79d48d79d48d9cea9c85de9179d48d79d48d%
  79d48d67c28b79d48d67c28b67c28b6cc78c72cd8d79d48d62bd8b72cd8d62bd8b67c28b50ac8853af8867c28b265381%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffffffffffffffffffffffffffff%
  85de91ffffffffffff9cea9cffffff9cea9c85de919cea9cffffffffffff9cea9c9cea9c72cd8d9cea9c6cc78c9cea9c%
  6cc78c67c28b72cd8d67c28b67c28b6cc78c72cd8d50ac8862bd8b62bd8b79d48d67c28b79d48d72cd8d67c28bffffff%
  79d48d62bd8b72cd8d5eb98a255681ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff%
  ffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff9cea9cffffff9cea9cffffffffffffffffff%
  ffffffffffff85de919cea9cffffffffffffffffffffffff9cea9cffffffffffff9cea9c9cea9c85de9172cd8d9cea9c%
